### 2020-03-08 Common/chapters/paper_reproduction.tex
Julien and Johan: new results and discussion with 2000 epochs (TL, global, ...) + minors
Johan and Julien: Resize one figure

\begin{figure}[!h]
\centering
\includegraphics[width=0.95\textwidth, keepaspectratio=true]{./figures/paper_reproduction_split.png}
\caption{Patient splitting process}
\label{fig:paper_reproduction_split}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=1\textwidth, keepaspectratio=true]{./figures/auc_our_test_set.png}
\caption{AUC of the best model on our test set}
\label{fig:paper_reproduction_auc_on_our_test_set}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[height=1\textwidth, keepaspectratio=true]{./figures/paper_reproduction_results_challenge1.png}
\caption{Score achieved in the PROSTATEx challenge using only our custom training set (80\% of all available data) for the training}
\label{fig:paper_reproduction_results_challenge_1}
\end{figure}

@@

Regarding the overall performance of the best model chosen at epoch 21, the latter generalizes well. This is particularly visible on the accuracy and AUC plots where the validation metrics are higher or equal to the training ones. The validation accuracy indicates that the model made the right class decision in approximately $75$\% of the time. Furthermore, since the model achieved a validation AUC of $0.76$, it shows that it had a good distinction capacity. In fact, the highest the AUC is, the highest is the ability of the model to predict benign lesions as benign and malignant lesions as malignant. Samuel G. et al. \cite{42} claim that a less-experienced radiologist can reach an AUC of $0.81$ and an expert an AUC of $0.91$. Consequently, this model is almost at the level of a radiologist, which is very promising. It is also important to keep in mind that the model was trained using only 164 patients (80\% of the 204 training patients), which suggests that even better results can be reached with more data.

>>>>

\begin{figure}[!h]
\centering
\includegraphics[width=1\textwidth, keepaspectratio=true]{./figures/paper_reproduction_split.png}
\caption{Patient splitting process}
\label{fig:paper_reproduction_split}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=0.6\textwidth, keepaspectratio=true]{./figures/auc_our_test_set.png}
\caption{AUC of the best model on our test set}
\label{fig:paper_reproduction_auc_on_our_test_set}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=0.6\textwidth, keepaspectratio=true]{./figures/paper_reproduction_results_challenge1.png}
\caption{Score achieved in the PROSTATEx challenge using only our custom training set (80\% of all available data) for the training}
\label{fig:paper_reproduction_results_challenge_1}
\end{figure}

@@

Regarding the overall performance of the best model chosen at epoch 21, the latter generalizes well. This is particularly visible on the accuracy and AUC plots where the validation metrics are higher or equal to the training ones. The validation accuracy indicates that the model made the right class decision in approximately $75$\% of the time. Furthermore, since the model achieved a validation AUC of $0.76$, it shows that it had a good distinction capacity. In fact, the highest the AUC is, the highest is the ability of the model to predict benign lesions as benign and malignant lesions as malignant. Armato. et al. \cite{42} claim that a less-experienced radiologist can reach an AUC of $0.81$ and an expert an AUC of $0.91$. Consequently, this model is almost at the level of a radiologist, which is very promising. It is also important to keep in mind that the model was trained using only 164 patients (80\% of the 204 training patients), which suggests that even better results can be reached with more data.
